Landscape heterogeneity simulation figures

### 2018-04-09 Manuscript_figures_2017_12_12.Rmd
Remove specific directory references

## Load and update summary dataset
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

@@

#Set working directory of where to produce Figures
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
```

@@

##Figure 1
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("Figure1_RF.tiff", height =10 , width =8.7, units = "cm", compression = "lzw", res = 1200)
multiplot(A, B, C, cols=1)
dev.off()

@@

##Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

@@

##Figure 2
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)

>>>>

## Load and update summary dataset
```{r}
#setwd()
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

@@

#Set working directory of where to produce Figures
#setwd()
```

@@

##Figure 1
Random forest variable importance results
```{r}
library(randomForest)
#setwd()

@@

#setwd()
tiff("Figure1_RF.tiff", height =10 , width =8.7, units = "cm", compression = "lzw", res = 1200)
multiplot(A, B, C, cols=1)
dev.off()

@@

##Figure 1- vertical
Random forest variable importance results
```{r}
library(randomForest)
#setwd()

@@

#setwd()
tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

@@

##Figure 2
Box plots rec rate vs. density
```{r}
setwd()
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
colnames(sub_data)[3]<-"d" #rename density as "d"
colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)
